---
title: "PSTAT 5LS Lab 7 Notes"
author: "Your Name Here"
date: "Winter 2025"
output: html_document
---

# Lab Notes

Use this place to take any notes during your lab section.

- Type any notes here
- Add new notes by using the dash `-` to create a list

# Lab Code

Use the chunks below to try out any code that you'd like. We have loaded the `penguins` data set for you in the first chunk, so you can try things out with this data.

```{r loadGentoo, error = T}
gentoo <- read.csv("gentoo.csv", stringsAsFactors = TRUE)
```

```{r tryIt1, error = T}
# Run this code chunk to have R run the regression and summarize the results. You'll need to change `y` and `x` in the code below to have R run the regression. Be sure to look at the code that your TA shares on their slides.
line1 <- lm(y ~ x, data = gentoo)
summary(line1)

```

```{r tryIt2, error = T}
# Run this code chunk to create a scatterplot of body mass on flipper length, including the regression line
plot(gentoo$body_mass_g ~ gentoo$flipper_length_mm,
     main = "Scatterplot of Body Mass versus Flipper Length for Gentoos",
     xlab = "Flipper Length (mm)",
     ylab = "Body Mass in (g)", 
     pch = 19)
abline(line1, col = "blue")

```

# Code Cheat Sheet

## `~`
- Read as "by"
- Used in side-by-side boxplots, scatterplots, and finding linear models
- `y ~ x` is the correct syntax for linear; `numeric_variable ~` categorical_variable` is the correct syntax for side-by-side boxplots

## `plot(y ~ x, data = data_name)`
- Used to create a scatterplot of the *y* variable by the *x* variable
- Can use the argument `data = data_name` to eliminate the need to specify where each of the variables *x* and *y* are contained

## `cor(x, y)`
- Finds the correlation coefficient between the numeric variable *x* and the numeric variable *y*

## `cor(numeric_data_frame)`
- Prints a correlation matrix for a data frame with all numeric variables

## `lm(y ~ x, data = data_name)`
- Finds the linear model between *x* and *y* from `data_name`
- You'll want to assign this a name in order to use it later

## `summary(linear_model_name)`
- Prints relevant values of a linear model

## `abline(linear_model_name)`
- Will plot the line found in `linear_model_name`

## Important plotting arguments

### `main = "Title of Your Graph in Double Quotes"`
- graph title that must be inside a set of double quotes

### `xlab = "x-axis Label of Your Graph in Double Quotes"`
- the x- (horizontal) axis label that must be inside a set of double quotes

### `ylab = "y-axis Label of Your Graph in Double Quotes"`
- the y- (vertical) axis label that must be inside a set of double quotes

