---
title: "PSTAT 5LS Lab 6 Notes"
author: "Your Name Here"
date: "Winter 2025"
output: pdf_document
---

# Lab Notes

Use this place to take any notes during your lab section.

- Type any notes here
- Add new notes by using the dash `-` to create a list

# Lab Code

Use the chunks below to try out any code that you'd like. 

```{r loadGentoo, error = T}
# Run this code chunk to make the `gentoo` data set available for analysis
gentoo <- read.csv("gentoo.csv", stringsAsFactors = TRUE)
```

```{r tryIt1, error = T}
# Run this code chunk to create a scatter plot with bill_length_mm as the 
# explanatory variable and body_mass_g as the response variable
plot(body_mass_g ~ bill_length_mm,
     data = gentoo,
     main = "Scatter plot of Body Mass versus Bill Length for Gentoos",
     xlab = "Bill Length (mm)",
     ylab = "Body Mass in (g)", 
     pch = 20)

```

```{r tryIt2, error = T}
# Run this code chunk to compute the correlation between bill_length_mm and body_mass_g
cor(gentoo$bill_length_mm, gentoo$body_mass_g)

```

```{r tryIt3, error = T}
# Run this code chunk to subset the `gentoo` data to contain only numeric variables. We will call this subset `numericGentoo`
numericGentoo <- subset(gentoo,
                          select = c("bill_length_mm", "bill_depth_mm", 
                                     "flipper_length_mm", "body_mass_g")
                          )

```

```{r tryIt4, error = T}
# Run this code chunk to make a correlation matrix of `numericGentoo`
cor(numericGentoo)

```

# Code Cheat Sheet

## `~`
- Read as "by"
- Used in side-by-side boxplots, scatter plots, and finding linear models
- `y ~ x` is the correct syntax for linear; `numeric_variable ~` categorical_variable` is the correct syntax for side-by-side boxplots

## `plot(y ~ x, data = data_name)`
- Used to create a scatter plot of the *y* variable by the *x* variable
- Can use the argument `data = data_name` to eliminate the need to specify where each of the variables *x* and *y* are contained

## `cor(x, y)`
- Finds the correlation coefficient between the numeric variable *x* and the numeric variable *y*

## `cor(numeric_data_frame)`
- Prints a correlation matrix for a data frame with all numeric variables

## Important plotting arguments

### `main = "Title of Your Graph in Double Quotes"`
- graph title that must be inside a set of double quotes

### `xlab = "x-axis Label of Your Graph in Double Quotes"`
- the x- (horizontal) axis label that must be inside a set of double quotes

### `ylab = "y-axis Label of Your Graph in Double Quotes"`
- the y- (vertical) axis label that must be inside a set of double quotes

